---
title: "Movies on Streaming Services"
author: "Team 39"
date: "11/21/2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library("knitr")
source("table.R")
source("chart1.R")
source("chart2.R")
source("chart3.R")
source("Summary Information Script.R")
```

### Introduction

Our group project takes a look at the movies domain. We want to explore various datasets, looking for whihc countries produce the most movies, which years had the most movies released, how many movies are on the different streaming services at the same time, and the differences between IMDB and rotten tomatoes ratings. These data points will help us understand more on various streaming services and movie production.

### Summary Paragraph

Our summary information function calculated having 9515 movies in the dataset. The United States produced 4650 movies (highest country) and Afghanistan has the least number of movies produced. 2019 had the most movies made in the year with 1014 movies. 1914 was the least with 1 movie. There are only 7 movies on all streaming platforms. Lastly, the highest difference between rotten tomatoes and IMDB's ratings was Jingle Pols (52%) and the lowest was I wish I was Here (same rating). 


```{r echo = FALSE}
answer_list()
```

### Summary Table

```{r echo = FALSE}
create_table()
```

### Charts
```{r echo = FALSE}
create_chart_1()
```

- The purpose of this chart is to see the movies each streaming services pick based on RottenTomatoes Rating
The x axis is the ratings where according the the official website, Rotten means less than 59, Fresh mean above 60, and Certified Fresh means above 75
- Observation: we can see that from the chart, if we apply the word 
“quality control” in this situation, overall, contents of movies on Hulu on average have better quality than the other two streaming services. Also, more than half of the movies on both Netflix and Prime are below 60/100.


```{r echo = FALSE}
create_chart_2()
```

- The purpose of this chart is to show the years of the movies on each streaming services
- Observation: all three of them are doing a good job adding new movies

```{r echo = FALSE}
create_chart_3()
```

- The purpose of this chart is to show the amount of movies on each streaming services
- Observation: if you like to watch movies, you can choose Netflix or Prime videos instead of Hulu or Disney plus
